---
title: "Extract data for climate mitigation project"
author: "Julia Blanchard, Camilla Novaglio, Derek Tittensor"
date: "2023-05-18"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Aim

This script is for extracting FishMIP global marine ecosystem model outputs for use in a cross-sectoral climate mitigation paper being led by Christoph Semken.

For this project we need th global time series of biomass outputs, spanning size ranges typical of exploited fishes - 10g to 1000 kg.

We will calculate annual time series spanning 1850-2100 under the rcp8.5 and rcp2.6 scenarios for each of the models, for whihc outputs are available:

APECOSM  - available, IPSL only
BOATS  - available
DBEM  - possible later to request OR possible using Lmax classes?
DBPM - available
EcoOcean  - possible using Lmax classes?
EcoTroph  - available?
FEISTY  - possible using Lmax classes?
MACROECOLOGICAL  - available
ZooMSS - available

```{r cars}
### Read in files and extract modelled data at global scale
library(raster)
library(ncfd4)
library(tidyverse)
library(ncdf4.helpers)
library(parallel)
library(pbapply)

### using files and code prepared by Cami:

dir<-"/rd/gem/private/users/camillan/EmergentConstraintData"

mem<-c("apecosm","boats", "dbpm", "zoomss", "ecotroph", "macroecological") 
esm<-c("gfdl-esm4", "ipsl-cm6a-lr")
scenario<-c("historical", "ssp126", "ssp585") 


# all 
combinations<-expand.grid(mem = mem, esm = esm, scenario = scenario) %>%
  mutate(resolution = ifelse(mem %in% c("zoomss", "ecotroph", "macroecological"), "annual", "monthly"), 
         year = case_when(
           mem %in% c("boats", "zoomss", "ecotroph", "macroecological") & scenario == "historical" ~ "1950_2014", 
           mem %in% c("apecosm", "dbpm") & scenario == "historical" ~ "1850_2014",
           scenario %in% c("ssp126", "ssp585") ~ "2015_2100"), 
         mem = as.character(mem), 
         esm = as.character(esm), 
         scenario = as.character(scenario),
         netcdf_name = paste0(paste(mem, esm, "nobasd", scenario, "nat_default_tcblog10_global", resolution, year, sep ="_"), ".nc"),
         esm_simpler = ifelse(esm == "ipsl-cm6a-lr", "ipsl","gfdl"),
         identifier = paste(mem, esm_simpler, scenario, sep ="_")) %>% 
  select(-esm_simpler) %>% 
  arrange(mem, esm, scenario)

# apply function in // ----

netcdf = combinations$netcdf_name

# function to be applied
extract_global_outputs<-function(netcdf,dir="/rd/gem/private/users/camillan/EmergentConstraintData"
){
  
 # # trial
  # netcdf = "ecotroph_gfdl-esm4_nobasd_historical_nat_default_tcblog10_global_annual_1950_2014.nc"
  # file = "new"

  if(file.exists(file.path(dir, netcdf))){
  
  ########## extract info from netcdf name
  model = sub("\\_.*", "", netcdf)
  
  if(str_detect(netcdf, "gfdl", negate = FALSE)){
    esm = "gfdl-esm4"
  }else if (str_detect(netcdf, "ipsl", negate = FALSE)){
    esm = "ipsl-cm6a-lr"
  }
  
  # WARNING - add in EC? 
  if(str_detect(netcdf, "monthly", negate = FALSE)){
    time_step = "monthly"
  }else if (str_detect(netcdf, "annual", negate = FALSE)){
    time_step = "annual"
  }
  
  if(str_detect(netcdf, "historical", negate = FALSE)){
    scenario = "historical"
  }else if (str_detect(netcdf, "ssp126", negate = FALSE)){
    scenario = "ssp1"
  }else if (str_detect(netcdf, "ssp585", negate = FALSE)){
    scenario = "ssp5"
  }else if (str_detect(netcdf, "picontrol|2100", negate = FALSE)) {
    scenario = "picontrol_fut"
  } else if (str_detect(netcdf, "picontrol|2014", negate = FALSE)) {
    scenario = "picontrol_hist"}
  
  # extract info from netcdf description: 
  nc_data <- nc_open(file.path(dir, netcdf))
  
  lon <- ncvar_get(nc_data, "lon")
  lat <- ncvar_get(nc_data, "lat", verbose = F)
  t <- as.character(nc.get.time.series(nc_data))
  
  # this is only to FIX zoom size bins names 
  if(model != "zoomss" & file == "new"){
    bins<-ncvar_get(nc_data, "bins")
  }else if (model != "zoomss" & file == "old"){ # this is only to check DBPM old files (not in DKRZ)
    bins<-ncvar_get(nc_data, "size")
  }else if (model == "zoomss"){
    bins<-c(1:6)}
  
  t_units<-ncatt_get(nc_data, "time", "units")$value
  b_units<-ncatt_get(nc_data, "tcblog10", "units")$value
  
  nc_close(nc_data)
  
  # print warnings 
  
  stLon<-lon[1]
  enLon<-lon[length(lon)]
  stLat<-lat[1]
  enLat<-lat[length(lat)]
  stTime<-t[1]
  enTime<-t[length(t)]
  
  if(stLon != -179.5){
    warning(paste(model, esm, scenario, "incorrect starting Lon", sep = " "), immediate. = TRUE)
  }
  if(enLon != 179.5){
    warning(paste(model, esm, scenario, "incorrect ending Lon", sep = " "), immediate. = TRUE)
  }
  if(stLat != 89.5){
    warning(paste(model, esm, scenario, "incorrect starting Lat", sep = " "), immediate. = TRUE)
  }
  if(enLat != -89.5){
    warning(paste(model, esm, scenario, "incorrect ending Lat", sep = " "), immediate. = TRUE)
  }
  if(scenario == "historical" & !stTime %in% c("1950-01-01","1850-01-01")){ # some model include 100 years more 
    warning(paste(model, esm, scenario, "incorrect starting time", sep = " "), immediate. = TRUE)
  }
  if(scenario != "historical" & !stTime %in% c("2015-01-01")){
    warning(paste(model, esm, scenario, "incorrect starting time", sep = " "), immediate. = TRUE)
  }
  if(scenario == "historical" & !enTime %in% c("2014-12-01", "2014-01-01")){ # models can be monthly or annual 
    warning(paste(model, esm, scenario, "incorrect ending time", sep = " "), immediate. = TRUE)
  }
  if(scenario != "historical" & !enTime %in% c("2100-12-01", "2100-01-01")){ # models can be monthly or annual 
    warning(paste(model, esm, scenario, "incorrect ending time", sep = " "), immediate. = TRUE)
  }
  if(t_units != "days since 1601-1-1 00:00:00"){
    warning(paste(model, esm, scenario, "incorrect time units", sep = " "), immediate. = TRUE)
  }
  if(bins[1] != 1 & bins[6] != 6){
    warning(paste(model, esm, scenario, "incorrect bins names", sep = " "), immediate. = TRUE)
  }
  if(bins[length(bins)] != 6){
    warning(paste(model, esm, scenario, "incorrect bins dimension", sep = " "), immediate. = TRUE)
  }
  if(b_units != "g m-2"){
    warning(paste(model, esm, scenario, "incorrect biomass units", sep = " "), immediate. = TRUE)
  }
 
  # extract data as raster object: 
  brick_data<-list()
 
  for (i in 1:length(bins)){
    brick_data[[i]]<-brick(file.path(dir, netcdf), level = i)
    print(dim(brick_data[[i]]))
  }
  

return(brick_data)
  }
  
} 
  
#test<-extract_global_outputs(netcdf[1],dir = dir)

# now do all:

cores<-detectCores()  -2

all_bricks<-pblapply(netcdf,extract_global_outputs,cl=cores)

## CHECK raster object - some combos don't exist
all_bricks[[4]][[1]]

# check map of first time slot
plot(all_bricks[[4]][[1]][[1]])

## NOW GET ANNUAL GLOBAL TIME SERIES FOR EACH MODEL AFTER SUMMMING ACROSS ALL LAYERS

## NEED TO CHECK WHICH LAYERS ARE PRESENT ACROSS ALL MODELS


  

```
