---
title: "Extract data for climate mitigation project"
author: "Julia Blanchard, Camilla Novaglio, Derek Tittensor"
date: "2023-05-18"
output: github_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Aim

This script is for extracting FishMIP global marine ecosystem model outputs for use in a cross-sectoral climate mitigation paper being led by Christoph Semken.

For this project we need th global time series of biomass outputs, spanning size ranges typical of exploited fishes - 10g to 1000 kg.

We will calculate annual time series spanning 1850-2100 under the rcp8.5 and rcp2.6 scenarios for each of the models, for whihc outputs are available:

APECOSM  - available, IPSL only
BOATS  - available
DBEM  - possible later to request OR possible using Lmax classes?
DBPM - available
EcoOcean  - possible using Lmax classes?
EcoTroph  - available?
FEISTY  - possible using Lmax classes?
MACROECOLOGICAL  - available
ZooMSS - available

## File dowload 

check FishMIP/EmergentConstraints repo R/01_extract_modelled_data.Rmd for details and notes. 

download macroecological (hist was dowloaded for SO project)

scp -r b381217@levante.dkrz.de:/work/bb0820/ISIMIP/ISIMIP3b/OutputData/marine-fishery_global/MACROECOLOGICAL/ipsl-cm6a-lr/future/*nat_default_tcblog10* /rd/gem/private/users/camillan/EmergentConstraintData/

scp -r b381217@levante.dkrz.de:/work/bb0820/ISIMIP/ISIMIP3b/OutputData/marine-fishery_global/MACROECOLOGICAL/gfdl-esm4/future/*nat_default_tcblog10* /rd/gem/private/users/camillan/EmergentConstraintData/ 

All models include 6 bins, except for boats and macroecological. Boats include 2-5 (with 1 and 6 being present but empty) and macroecological includes bins 1 to 5. Sums across layers are calculated using bins 2 to 5, minimum common denominator.

## Set environment 

```{r cars}

rm(list=ls())

### Read in files and extract modelled data at global scale
library(raster)
library(ncdf4)
library(tidyverse)
library(ncdf4.helpers)
library(parallel)
library(pbapply)
library(dplyr, warn.conflicts = FALSE)

select<-dplyr::select 

```

## Read in files and extract modelled data at global scale

```{r}

### using files and code prepared by Cami:

dir<-"/rd/gem/private/users/camillan/EmergentConstraintData"

mem<-c("apecosm","boats", "dbpm", "zoomss", "ecotroph", "macroecological") 
esm<-c("gfdl-esm4", "ipsl-cm6a-lr")
scenario<-c("historical", "ssp126", "ssp585") 

# all file combinations

combinations<-expand.grid(mem = mem, esm = esm, scenario = scenario) %>%
  mutate(resolution = ifelse(mem %in% c("zoomss", "ecotroph", "macroecological"), "annual", "monthly"), 
         year = case_when(
           mem %in% c("boats", "zoomss", "ecotroph", "macroecological") & scenario == "historical" ~ "1950_2014", 
           mem %in% c("apecosm", "dbpm") & scenario == "historical" ~ "1850_2014",
           scenario %in% c("ssp126", "ssp585") ~ "2015_2100"), 
         mem = as.character(mem), 
         esm = as.character(esm), 
         scenario = as.character(scenario),
         netcdf_name = paste0(paste(mem, esm, "nobasd", scenario, "nat_default_tcblog10_global", resolution, year, sep ="_"), ".nc"),
         esm_simpler = ifelse(esm == "ipsl-cm6a-lr", "ipsl","gfdl"),
         identifier = paste(mem, esm_simpler, scenario, sep ="_")) %>% 
  select(-esm_simpler) %>% 
  arrange(mem, esm, scenario)

# apply function in // ----

netcdf = combinations$netcdf_name

source("/home/ubuntu/climate_mitigation/R/Helper_functions_mitigation.R")

# # test function 
# test<-extract_global_outputs(netcdf[4]) 
# 
# # check
# test$brick_data_annual
# plot(test$brick_data_annual[[5]][[10]]) # size bin 5, random time step
# 
# rm(test)

# now do all:
all_bricks<-pblapply(netcdf,extract_global_outputs,cl=detectCores()-2)

# extract data from function object
names(all_bricks) <- combinations$identifier

# extract data from function objects
# annual maps as raster objects
brick_data_annual<-sapply(all_bricks, function(x) x[["brick_data_annual"]])
brick_data_annual[sapply(brick_data_annual, is.null)] <- NULL # remove empty objects

# # check
# names(brick_data_annual)
# brick_data_annual$boats_gfdl_historical[[3]][[1]]
# plot(brick_data_annual$boats_gfdl_historical[[3]][[1]])

# annual trend in biomass at size bins level, for each MEM, ESM and scenario combination
SumsBySizeBins_df<-sapply(all_bricks, function(x) x[["SumsBySizeBins_df"]])
SumsBySizeBins_df[sapply(SumsBySizeBins_df, is.null)] <- NULL

# # check
# SumsBySizeBins_df$boats_gfdl_historical

# adjust dataset: 
SumsBySizeBins_df<-do.call(rbind, SumsBySizeBins_df)
rownames(SumsBySizeBins_df)<-NULL
SumsBySizeBins_df<-SumsBySizeBins_df %>% 
  select(Year,scenario, esm, mem, bin, weighted_mean) %>% 
  rename(year = Year, biomass = weighted_mean)
  
head(SumsBySizeBins_df)

# annual trend in total biomass (sum across size bins 2 to 5), for each MEM, ESM and scenario combination
SumsAllBio_df<-sapply(all_bricks, function(x) x[["SumsAllBio_df"]])
SumsAllBio_df[sapply(SumsAllBio_df, is.null)] <- NULL

# # check
# SumsAllBio_df$boats_gfdl_historical

# adjust dataset: 
SumsAllBio_df<-do.call(rbind, SumsAllBio_df)
rownames(SumsAllBio_df)<-NULL
SumsAllBio_df<-SumsAllBio_df %>% 
  select(Year,scenario, esm, mem, weighted_mean_allBio) %>% 
  rename(year = Year, biomass = weighted_mean_allBio)
  
head(SumsAllBio_df)

```

## save data as temp_file 

```{r}

save(brick_data_annual,
     SumsBySizeBins_df,
     SumsAllBio_df,
     file = "/home/ubuntu/climate_mitigation/Tmp_data/Extract_global_MEMs.RData")

```

## check outputs 

```{r}

rm(list=ls())
data<-"/home/ubuntu/climate_mitigation/Tmp_data/Extract_global_MEMs.RData"
load(data)

# plot all 
SumsBySizeBins_df_toplot<- SumsBySizeBins_df %>% 
  mutate(ID = paste(esm, bin, scenario, sep ="_"))

plot<-ggplot(SumsBySizeBins_df_toplot, aes(x = year, y = biomass, group = ID, color = scenario))+
  geom_line()+
  facet_wrap(~mem)

jpeg("/home/ubuntu/climate_mitigation/Output/trends_allModels_allBinsSeparately.jpg", width = 7, height = 5, units = "in", res = 300, bg = "transparent")
plot
dev.off()

# plot biomass tot 
SumsAllBio_df_toplot_ipsl<- SumsAllBio_df %>% 
  filter(esm == "ipsl-cm6a-lr")

plot_ipsl<-ggplot(SumsAllBio_df_toplot_ipsl, aes(x = year, y = biomass, group = scenario, color = scenario))+
  geom_line()+
  theme_bw()+
  ggtitle("IPSL")+
  facet_wrap(~mem, scale = "free")

SumsAllBio_df_toplot_gfdl<- SumsAllBio_df %>% 
  filter(esm != "ipsl-cm6a-lr")

plot_gfdl<-ggplot(SumsAllBio_df_toplot_gfdl, aes(x = year, y = biomass, group = scenario, color = scenario))+
  geom_line()+
  theme_bw()+
  ggtitle("GFDL")+
  facet_wrap(~mem, scale = "free")

library(patchwork)

jpeg("/home/ubuntu/climate_mitigation/Output/trends_allModels_allBinsSummed.jpg", width = 8, height = 8, units = "in", res = 300, bg = "transparent")
plot_ipsl/plot_gfdl
dev.off()

# check apecosm 
SumsAllBio_df_toplot2<-SumsAllBio_df %>% 
  filter(mem == "apecosm", esm == "ipsl-cm6a-lr", scenario == "historical")

plot<-ggplot(SumsAllBio_df_toplot2, aes(x = year, y = biomass))+
  geom_line()

# check this is the same as per JB and DT (see test)
jpeg("/home/ubuntu/climate_mitigation/Output/test_apecosm_CNcode.jpg", width = 7, height = 5, units = "in", res = 300, bg = "transparent")
plot
dev.off()

## plot maps of values 
plot(brick_data_annual$dbpm_ipsl_historical[[1]][[1]])
plot(brick_data_annual$apecosm_ipsl_historical[[1]][[1]])

```

## print .csv 

```{r}

write.csv(SumsAllBio_df,
     file = "/home/ubuntu/climate_mitigation/Tmp_data/Extract_global_MEMs_SumsAllBio_df.csv",
     row.names = FALSE)

```

